A survey of HTTP caching options on the open Semantic Web

### 2015-01-19 sanity/paper1.tex
Remove URIs
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1009 43ef1190-90fd-4dd7-a769-d0121f02b80e

\subtitle{---Unpublished Working Draft, do not circulate---}

@@

The Billion Triple Challenge 2014 dataset provided data in the form of
NQuad files. Due to the presence of invalid RDF, we iterated through
the NQuad files on a line-by-line basis. First, we matched each line
against a regular expression were lines matching
\texttt{ontology|endpoint|sparql|vocabular} passed the filter. Then,
the Perl framework
RDF::Trine\footnote{https://metacpan.org/release/GWILLIAMS/RDF-Trine-1.011} was used
to parse the line. Lines that failed to parse was discarded. We have
not investigated whether this could introduce biases. Statements were
then accepted into a new NQuad file if they had a predicate that
matched the
\rdfterm{sd:endpoint}\footnote{http://www.w3.org/TR/sparql11-service-description/\#sd-endpoint}
or matched a case-insensitive regular expression \texttt{sparql} if
the subject and objects were both resources, or the predicates
\rdfterm{void:vocabulary}\footnote{http://www.w3.org/TR/void/\#vocabularies},
\rdfterm{rdfa:vocabulary}\footnote{http://www.w3.org/TR/rdfa-core/\#term-prefix-definitions-vocabulary}
or
\rdfterm{api:vocabulary}\footnote{http://purl.org/linked-data/api/vocab\#vocabulary},
as well as having a resource as object. Finally, statements with the
the classes
\rdfterm{cogs:Endpoint}\footnote{http://vocab.deri.ie/cogs\#Endpoint},
\rdfterm{owl:Ontology} and
\rdfterm{voaf:Vocabulary}\footnote{http://lov.okfn.org/vocab/voaf/v2.3/index.html\#Vocabulary}
in the object position were also accepted. More classes and properties
were considered, but not used in the data reduction if they did not
occur in the original data.

>>>>

%\subtitle{---Unpublished Working Draft, do not circulate---}

@@

The Billion Triple Challenge 2014 dataset provided data in the form of
NQuad files. Due to the presence of invalid RDF, we iterated through
the NQuad files on a line-by-line basis. First, we matched each line
against a regular expression were lines matching
\texttt{ontology|endpoint|sparql|vocabular} passed the filter. Then,
the Perl framework
RDF::Trine\footnote{https://metacpan.org/release/GWILLIAMS/RDF-Trine-1.011}
was used to parse the line. Lines that failed to parse were
discarded. We have not investigated whether this could introduce
biases. Statements were then accepted into a new NQuad file if they
had a predicate that matched the \rdfterm{sd:endpoint} or matched a
case-insensitive regular expression \texttt{sparql} if the subject and
objects were both resources, or the predicates
\rdfterm{void:vocabulary}, \rdfterm{rdfa:vocabulary}, or
\rdfterm{api:vocabulary}, as well as having a resource as
object. Finally, statements with the the classes
\rdfterm{cogs:Endpoint}, \rdfterm{owl:Ontology} and
\rdfterm{voaf:Vocabulary} in the object position were also
accepted\footnote{LOV may be used to resolve these prefixed
  names}. More classes and properties were considered, but not used in
the data reduction if they did not occur in the original data.
